### 2018-10-03 paper/related.tex

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, Tor~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, these efforts principally aimed at enabling dissemination to many users who do not necessarily know each other in person. With \ac{SPORES}, we focus on sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of users that out-of-band agree to share a file but do not keep it available for anyone else in the future.

@@

Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage. They do not, however, allow for unreliable user devices as relay nodes, as we do.

>>>>

P2P file sharing has been researched extensively, with respect to aspects such 
as architecture (starting with the semi-centralized Napster, then decentralized 
Gnutella), availability and replication~\cite{replica}, scalability 
(Bittorrent~\cite{bittorrent-incentives}), anonymity 
(Freenet~\cite{Clarke:2001}, \ac{Tor}, and \acp{DHT} such as CAN, Chord, 
Pastry, and Tapestry, see~\cite{dhtchurn} for an overview). In contrast to our 
work, these efforts principally aimed at enabling dissemination to many users 
who do not necessarily know each other in person. With \ac{SPORES}, we focus on 
sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of 
users that out-of-band agree to share a file but do not keep it available for 
anyone else in the future.

@@

Onion routing schemes, with infrastructure and governance (\ac{Tor}) and 
without (I2P\footnote{https://geti2p.net/en/}), though geared toward web 
browsing, come closest to file transfer without third-party storage. They do 
not, however, allow for unreliable user devices as relay nodes, as we do.
